---
title: "Demo Content"
output: html_document
---

```{r setup, include=FALSE}
library(connectwidgets)
library(dplyr)
library(magrittr)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

client <- connect(
  server  = Sys.getenv("CONNECT_SERVER"),
  api_key = Sys.getenv("CONNECT_API_KEY")
  )

all_content <- client %>%
  content() %>%
  arrange(desc(updated_time))
```


## R

### Shiny App
```{r shiny}
all_content %>%
  filter(title == "Demo Shiny Penguins") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/SamEdwardes/demo-shiny-penguins)

### RMarkdown
```{r rrmarkdown}
all_content %>%
  filter(title == "Demo rmd Penguins") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/SamEdwardes/demo-rmd-penguins)

### Plumber API
```{r plumber}
all_content %>%
  filter(title == "Demo - Palmer Penguins - Plumber API") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/SamEdwardes/demo-plumber-penguins)

### Pins

A demo of using pins with RStudio pro products.
```{r pins}
all_content %>%
  filter(guid == "a84b4b78-537f-42a3-827c-7b377ee656d7") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/SamEdwardes/demo-pins-r-penguins/blob/main/app/report.Rmd)

---

## Python

### Jupyter Notebook

Jupyter notebook with interactive visualizations
```{r jupyter}
all_content %>%
  filter(title == "Jupyter Interactive Visualization") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/jupyter-interactive-visualization)

### Flask API

Model trained in spaCy via a Flask API
```{r flask}
all_content %>%
  filter(title == "Flask Sentiment Analysis API") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/flask-sentiment-analysis-api)


### Fast API

Fast API demo based on stock data
```{r fast}
all_content %>%
  filter(title == "Fast API Demo") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/fastapi-stock)


### Dash App

Dash Demo App
```{r dash}
all_content %>%
  filter(title == "Dash Demo App") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/dash-app)


### Streamlit App

Streamlit Demo showing income share
```{r streamlit}
all_content %>%
  filter(title == "Streamlit Demo Income Share") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/streamlit-income-share)

### R Markdown with Python

Integration of Python into R projects with reticulate
```{r rmarkdownpython}
all_content %>%
  filter(title == "R Markdown with Python") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/blob/main/rmarkdown-notebook/rmarkdown-notebook.Rmd)


---

## Bike Predict (R)

### Predict Shiny App
```{r bikepredict}
all_content %>%
  filter(title == "Bike Predict - App - Client App") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/python-examples/tree/main/jupyter-interactive-visualization)

### Web Data to Pins & Database
```{r webtopins}
all_content %>%
  filter(title == "Bike Predict - ETL Step 1 - Raw Data Refresh") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/bike_predict/blob/main/content/01-etl/01-raw-data-refresh/document.qmd)

### Train and Deploy Model (vetiver, pins, plumber, connect)
```{r deploy}
all_content %>%
  filter(title == "Bike Predict - Model Step 1 - Train and Deploy") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/bike_predict/blob/main/content/02-model/01-train-and-deploy-model/document.qmd)

### Model Monitoring and Accuracy (vetiver, pins, plumber, connect)
```{r metrics}
all_content %>%
  filter(title == "Bike Predict - Model Step 2 - Metrics") %>%
  slice(1) %>%
  rsc_card()
```
[Code URL](https://github.com/sol-eng/bike_predict/blob/main/content/02-model/02-model-metrics/document.qmd)




[Source code](https://github.com/sol-eng/bike_predict/blob/main/content/02-model/02-model-metrics/document.qmd) to this connectwidget dashboard.


